Create Walkover of Brief Names

### 2022-04-07 data-cleaning/04-create-walkover-brief-name.Rmd
add june v russo fix

```{r}
check_in_amicus <- amicus %>% left_join(data, by = c('brief' = 'name_correct'))
june_russo_fix <- check_in_amicus %>% filter(is.na(name_incorrect)) %>%
  select(brief) %>% unique()
```

>>>>

Add our updated brief id

```{r}
amicus_current_ids <- amicus %>% select(brief, brief_id = id)
final <- data %>% 
  left_join(amicus_current_ids, c("name_correct" = "brief")) %>% 
  select(new_id=brief_id, name_correct, name_incorrect, old_id = id)

final %>% filter(is.na(new_id)) # this brief doesn't exist in our data ?
```

## June v Russo

Read in the June v Russo names from Holly's data file.

```{r}
jvr_incorrect <- box_read_excel("941695019313", sheet="final") 
#jvr_incorrect %>% head()
```

Get the "correct" june v russo brief names

```{r}
jvr_correct <- amicus %>% filter(grepl("June", brief)) %>%
  mutate(id = as.double(id)) %>% 
  select(new_id=id,name_correct=brief)
```

Join the two

```{r}
jvr <- jvr_correct %>% left_join(jvr_incorrect, c("new_id"="brief_id"))

jvr <- jvr %>% 
  mutate(old_id = 0) %>% 
  select(new_id, name_correct, name_incorrect=amicus, old_id)
```

Add to final df

```{r}
final <- final %>% rbind(jvr) %>%
  distinct(new_id, name_correct, name_incorrect, old_id)
```

## Save
